---
title: "Isaiah's R package"
author: "Isaiah Pugh"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Congratulations for getting this far. To complete the evidence that you have made a working R package please answer the following by using the supplied rmd and upload the knitted html to CANVAS.

I will assume your package is called **isaiahpackage** and you have packaged and documented functions `myboot`, `myci`, `mycltp` and `mydbinom`.


# First function

Please place your first function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r first}
ddt = read.csv("DDT.csv")
isaiahpackage::myboot2(x = ddt$DDT)
```


# Second function

Please place your second function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r second}
x = rnorm(30,mean=10,sd=12)
isaiahpackage::myci(x)
```


# Third function

Please place your third function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r third}
isaiahpackage::mycltp(10,10000)
```


# Forth function

Please place your forth function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r forth}
isaiahpackage::mydbinom(1:10,100,0.5)
```

# The github repository



This is the address of my GITHUB repository:
<https://github.com/GvldenPharaoh/Rpackage.git>

Replace this with your own address.
